Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2016-01-07 paper/paper_acm.tex

The work on forcing in type theory~\cite{jaber2012extending} also
gives a computational meaning to a type theory enriched with new
logical or computational principle, but for other kinds of principles
as the ones interpreted by LT-sheafification.
%
Actually, forcing is entirely complementary to LT-sheafification as
forcing corresponds to the presheaf construction while
LT-sheafification corresponds to the topological transformation that
allows to go from the presheaf to the sheaf construction.

@@

Section~\ref{sec:lawv-tiern-nutshell} presents an overview of the construction. 
% 
Section~\ref{sec:hott} presents the foundations of homotopy type theory
and present a analogous of~\cite[Corollary 6.2.3.5]{lurie}. 
%
Section~\ref{sec:lexmod} introduces the notion of left-exact stratified
modalities, on which this paper is based.
%
Section~\ref{sec:sheaves} defines Lawvere-Tierney sheaves in homotopy
type theory.
%
Section~\ref{sec:sheafification} explains the construction of the
LT-sheafification functor.
%
The definitions of this paper uses an informal presentation of
homotopy type theory, working entirely inside of Univalent
Foundations. 
 %
Section~\ref{sec:formalization} discusses the details of the
formalization in Coq using formal type theory, in particular issues
concerning universe polymorphism.
%
Finally, Section~\ref{sec:future-works} concludes on future works.

@@

>>>>

The work on forcing in type theory~\cite{jaber2012extending} also
gives a computational meaning to a type theory enriched with new
logical or computational principle, but for other kinds of principles
as the ones interpreted by LT-sheafification.
%
Actually, forcing is entirely complementary to LT-sheafification as
forcing corresponds to the presheaf construction while
LT-sheafification corresponds to the topological transformation that
allows to go from the presheaf construction to the sheaf construction.

@@

Section~\ref{sec:lawv-tiern-nutshell} presents an overview of the
construction.
% 
Section~\ref{sec:hott} presents the foundations of homotopy type theory
and presents a analogous of~\cite[Corollary 6.2.3.5]{lurie}. 
%
Section~\ref{sec:lexmod} introduces the notion of left-exact stratified
modalities, on which this paper is based.
%
Section~\ref{sec:sheaves} defines Lawvere-Tierney sheaves in homotopy
type theory.
%
Section~\ref{sec:sheafification} explains the construction of the
LT-sheafification functor.
%
The definitions of this paper use an informal presentation of
homotopy type theory, working entirely inside of Univalent
Foundations. 
 %
Section~\ref{sec:extension-type} describes how to use this
construction to define a modality on $\Type$ from a modality on
$\HProp$.
%
Section~\ref{sec:formalization} discusses the details of the
formalization in Coq using formal type theory, in particular issues
concerning universe polymorphism.
%
Finally, Section~\ref{sec:future-works} concludes on future works.

@@

In order to understand the construction of LT-sheafification in homotopy
type theory, we first briefly recall the corresponding construction in
topos theory and then gives an overview of our construction.
